OG_cleaning

### 2019-07-02 OG_cleaning.Rmd
add OG cleaning functions

>>>>

```{r create new combo variables from exported boolean phenotype}
l<-lapply(ls(pattern="bulk_summary"), function(x) get(x))
l<-lapply(l, function(x) sum_boolean(x))
filenames<-ls(pattern="bulk_summary")
for(i in 1:5){
assign(filenames[i], data.frame(l[i]))}

l<-lapply(ls(pattern="_OG"), function(x) get(x))
l<-lapply(l, function(x) sum_boolean(x))
filenames<-ls(pattern="_OG")
for(i in 1:9){
assign(filenames[i], data.frame(l[i]))}
```

```{r}
l<-lapply(ls(pattern="bulk_summary"), function(x) get(x))
l<-lapply(l, function(x) OG_background.subtract(x, "Donor", "Stim", "UN", "OG_freq"))
filenames<-ls(pattern="bulk_summary")
for(i in 1:5){
assign(filenames[i], data.frame(l[i]))}
```
